### 2019-02-22 paper/intro-notes.tex
Write up on differential stopping behavior

 families are more likely to cease childbearing after the birth of 
a son than after a daughter \citep{Das1987,Arnold1997,arnold98,clark00,dreze01,Basu2010}.

Parents are also more likely to cease childbearing after the birth of 
a son than after a daughter 
\citep{repetto72,ben-porath76b,Das1987,Arnold1997,arnold98,clark00,dreze01,filmer09,Basu2010,Altindag2016}.
}

>>>>

There is amble evidence that son preference has affected individual families' fertility
decisions in India and elsewhere.
It is, for example, clear that a significant proportion of Indian families follow a
son preference based differential stopping behavior, where, for a given number of
children, they are more likely to have an additional child if they have not yet
reached their preferred number of sons 
\citep{repetto72,Das1987,Arnold1997,clark00,Basu2010,Barcellos2014}.
A smilar pattern is found in many other countries 
\citep[see, for example][]{larsen98,filmer09,Altindag2016}.%
\footnote{
One potential effect of this behavior is that girls tend to end up in larger families, 
which may have negative impacts on survival and human capital investments, even in 
the absence of direct discrimination \citet{Jensen2003,Kugler2017}.
}

Of more direct interest here is differential \emph{spacing} behavior, both because 
it has been used as a measure for son preference and because birth spacing may directly
impact health and other outcomes for both children and mother.
